Stimuli List Generation

### 2023-03-06 Stimuli List and Data Source/Stimuli List Generation.Rmd
updated stimuli list code
small edits

  # Exporting dfs (to create stimuli lists in word)
  rio::export(data_random, paste("New_Phrase_List", i, ".csv"))
}

@@

# Merging the two lists together

@@

# Creating the soundFile and number of target words variables

>>>>

  # Exporting dfs (to create stimuli lists in word)
  rio::export(data_random, paste("New_Phrase_List", i, ".csv", sep = ""))
}

@@

# Merging the two lists together.

@@

# Creating the soundFile and number of target words variables.
